Extracting The Power of Dependent Types

### 2021-07-09 paper.tex
Add paragraph on limitations to introduction

>>>>

\paragraph{Limitations}

While we claim our approach is flexible and powerful, it is
certainly not a magic bullet. There are still a lot of things that
need to be implemented for each target language: the language
embedding itself, the encoding of the properties under consideration
as types in the host language, and the extractor that transforms
embedded programs back into the syntax of the original language.  For
enforcing more complex properties, it might also be necessary to write
proofs to convince the typechecker of the host language that they are
indeed satisfied.
%
The main advantage of our approach is twofold: first, it allows
you to implement all these things --- as well as the embedded programs
themselves --- \emph{side by side in a single language}, simplifying
the development. And secondly, it allows you to reuse the typechecker
and evaluator of the host language, saving you a lot of work.  In the
end, our goal is not to showcase a single example but to empower you
to apply this approach yourself to verify code in any language.
